Identity Blockchain - Proof of Identity

### 2022-07-26 paper.tex

		uint previousKey = ninKidUsed[hNin];
		if (previousKey == vKid) return; // already registered

		uint previousVKid = ninKidUsed[hNin];
		if (previousVKid != vKid && invalidateKid == true) {
			// If they are different, invalidate old Kid
			kidInvalid[previousVKid] = true;
		}
		require(!kidInvalid[vKid]);

>>>>

		uint previousVKid = ninKidUsed[hNin];
		if (previousVKid == vKid) return; // already registered
		if (previousVKid != vKid && invalidateKid == true) {
			// If they are different, invalidate old Kid
			kidInvalid[previousVKid] = true;
		}
		require(!kidInvalid[vKid]);
